% !TEX root = ../main.tex
\newpage
\section*{Nomenclature}
\addcontentsline{toc}{subsection}{Nomenclature}
\vspace{-.5cm}
\begin{alignat*}{2}
& \ic &&\text{Imaginary unit.}\\
&e \text{ (or} \exp\text{)} &&\text{Euler's number.}\\ \\
& n&&\text{Network node.}\\
& N &&\text{Network degree. The number of nodes in the network.}\\
& A_{ij} &&\text{Adjacency matrix. Models which node $i$ is connected to node $j$ and vice-versa.}\\
& \kmean &&\text{Average node degree in the network.}\\
& \degree(n) = \k &&\text{Degree of node $n$, as a vector of the in- and out-degree $\left(\kin, \kout \right)$.}\\
& \kinb, \koutb && \text{Node degree vector of all in- and out degrees of the network.} \\
& M_{\k} &&\text{Number of unique node degrees in the network. Cardinality of $\K$.}\\
& P(k), P(\k) &&\text{Univariate and bivariate network degree distribution.}\\
&\kmin, \kmax &&\text{Smallest and largest degree in a network.}\\ 
&\gamma &&\text{Degree exponent of a scale-free network.}\\ 
&p &&\text{Probability threshold of forming a link in random networks.}\\ \\
&\theta_i(t) &&\text{Phase variable function of the theta model (of neuron $i$).}\\
& \Pulse_s (\theta)&&\text{Pulse-shaped synaptic coupling function with sharpness } s \text{.}\\
&\kappa &&\text{Macroscopic coupling strength.}\\
&\eta_i, I_i(t) &&\text{Excitability threshold and input current (of neuron $i$).}\\
&g(\eta \rvert \k) \quad &&\text{Excitability threshold distribution with mean $\eta_0(\k)$ and width $\sigma(\k)$.}\\ \\
& Z(t) &&\text{Kuramoto order parameter function.}\\
& z(\k, t) &&\text{Synchronisation dynamics function for nodes of degree $\k$.}\\
& \bar{Z}(t) &&\text{Mean field order parameter function for arbitrary networks.}\\ \\
& S_i^{\rm in}(t), S_i^{\rm out}(t)\quad &&\text{Spike trains received and emitted by neuron $i$ as a sum of delta functions in time.}\\ 
& K_{ij} &&\text{Coupling matrix. Strength of the synaptic connections between neurons $i$ and $j$.}\\
& \Delta t_{ij} &&\text{Time difference between spikes of neurons $i$ and $j$.}\\
& W(t) &&\text{Learning window. Correlation between change in synaptic strength and spike times.}\\ 
& \phi(t) &&\text{IP learning function. Correlation between excitability strength and spike times.}\\ \\
& \T &&\text{Set of angles in [-$\pi$, $\pi$[.}\\
& \K &&\text{Set of $M_{\k}$ unique degrees in a network, support of $P$.}\\ 
& \R, \c &&\text{Set of real and complex numbers.}\\ 
&  \C && \text{Set in the complex unit circle so that $\C = \{ z \in \c : \: \rvert z \rvert \leq 1 \} $.} \\ \\
& \permute(v), \permuteinv(v) &&\text{Random permutation and inverse permutation of the elements of a vector $v$.}\\ 
\end{alignat*}
